---
pagetitle: "Experimental Design Results"
date: ""
output: html_document
params: 
  name: NA
  site: NA
  species: NA
  spp_num: NA
  treatments: NA
  restor_prop: NA
  survival_data: NA
---

<style>
div.blue {background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>

# Design for `r params$name`
### `r format(Sys.Date(), format="%d-%b-%Y")`

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
### REMOVE THIS SECTION WHEN RUNNING THE ACTUAL THING
name <- "Baltra New"
species <- c("Opuntia echios var. echios","Acacia macracantha")
species_num <- c(30,40)
treatments <- c("control", "treatment1", "treatment2")
restor_prop <- 0.5
source("scripts/00_functions.R")
survival_data <- read_csv("data/hypothetical_data.csv")

# source("00_code_functions.R")
# source("00_functions_B.R")

```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# The `params` object is available in the document.
params$name
params$species

# remove white space from spp_number string:
species_num <- str_replace_all(params$spp_num, fixed(" "), "")
# then separate by comma:
species_num <- as.numeric(str_split(species_num, ",")[[1]])
species_num
```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# all_sites <- design_sites(spp2plant=c("Lycium minimum","Opuntia echios var. echios", "Maytenus octogona"),
#                           site_params = list(site1=list(numbers=c(14,10,13), total_groasis=20, total_cocoon=999, zone_type="arid")),
#                           sample_sizes=samp_sizes, recomendations=recs, overall_results=overall_res, zone_recom=zone_recs)

all_sites <- design_sites(spp2plant=params$species,
                          site_params = list(site1=list(numbers=species_num,
                                                        total_groasis=params$gro_num,
                                                        total_cocoon=params$coc_num,
                                                        zone_type=params$zone_type,
                                                        isle=params$island)),
                          sample_sizes=params$samp_sizes,
                          recomendations=params$recs,
                          overall_results=params$overall_res,
                          zone_recom=params$zone_recs,
                          restor_prop=params$restor_prop)

# ### REMOVE THIS SECTION AND UNCOMMENT THE PREVIOUS ONE WHEN RUNNING THIS FOR REAL
# all_sites <- design_sites(spp2plant=species,
#                           site_params = list(site1=list(numbers=species_num, 
#                                                         total_groasis=gro_num, 
#                                                         total_cocoon=coc_num, 
#                                                         zone_type=zone_type)),
#                           sample_sizes=samp_sizes, 
#                           recomendations=recs, 
#                           overall_results=overall_res, 
#                           zone_recom=zone_recs)

all_sites_sub <- all_sites$site1
trt_totals <- apply(all_sites_sub[,-1], 2, sum)
coc_total <- sum(trt_totals[grepl("cocoon", names(trt_totals))])
gro_total <- sum(trt_totals[grepl("groasis", names(trt_totals))])
hyd_total <- sum(trt_totals[grepl("hydro", names(trt_totals))])
cont_total <- sum(trt_totals[names(trt_totals) == "hydrogel" | grepl("contr", names(trt_totals))])
plants_tot <- sum(trt_totals)
species <- all_sites_sub[,1]
spp_totals <- tibble(species=species, total=apply(all_sites_sub[,-1], 1, sum))
```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
### Now make a function that creates a list for each site by creating a row for each
### combination of species and technologies and ordering them randomly in order to plant them randomly:
# treatments:
trtmt <- c("control", "hydrogel", "cocoon", "cocoon_hydrogel", "groasis", "groasis_hydrogel")
sites_bound <- bind_rows(all_sites, .id = "site")
species <- unique(sites_bound$species)
all_site_plantings <- list()
for(site_name in names(all_sites)){
  # sites <- names(all_sites)
  # site_name <- sites[1]
  site <- all_sites[[site_name]]
  site <- as.data.frame(site)
  
  site_stack <- NULL
  for(sp in species){
    species_stack <- NULL
    for(i in trtmt){
      spp <- filter(site, species==sp)
      Species <- rep(spp[,1], spp[,i])
      Treatment <- rep(i, spp[,i])
      trt_stack <- data.frame(Species,Treatment)
      species_stack <- rbind(species_stack, trt_stack)
    }
    site_stack <- rbind(site_stack, species_stack)
  }
  random_rows <- sample(nrow(site_stack))
  
  site_planting_table <- site_stack[random_rows,]
  
  all_site_plantings[[site_name]] <- site_planting_table
}
random_plantings <- all_site_plantings$site1

### FOR CREATING HTML TABLES: https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

```

## Experimental Design:

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
all_sites_sub %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left", font_size = 16)
```

## Previous Plantings on `r params$island`

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
samp_sub_fin <- NULL
for(s in params$species){
  samp_sub <- filter(params$samp_sizes, island==params$island & species_full==s) %>%
    select(treatment, size)
  # samp_sub <- filter(params$samp_sizes, island=="Floreana" & species_full=="Zanthoxylum fagara") %>%
  #   select(treatment, size)
  
  treatments <- samp_sub$treatment
  samples <- samp_sub$size
  samp_sub <- as.tibble(t(samp_sub))
  names(samp_sub) <- treatments
  samp_sub <- samp_sub[-1,] %>%
    mutate(control = as.numeric(control),
           hydrogel = as.numeric(hydrogel),
           cocoon = as.numeric(cocoon),
           cocoon_hydrogel = as.numeric(cocoon_hydrogel),
           groasis = as.numeric(groasis),
           groasis_hydrogel = as.numeric(groasis_hydrogel),
           species=s) %>%
    select(species, everything())
  
  samp_sub_fin <- rbind(samp_sub_fin,samp_sub)
}

samp_sub_fin %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left", font_size = 16)
```

---

### Treatment and species totals:

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
tibble(treatment = names(trt_totals), total=trt_totals) %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "float_left", font_size = 16)

spp_totals %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left", font_size = 16)
```
<br><br><br><br><br><br><br>
 
### Total number of technologies required:

<div class = "blue">

### Total Cocoons: **`r coc_total`**

### Total Groasis: **`r gro_total`**

### Total Hydrogels: **`r hyd_total`**

<!-- ### Total No-technologies: **`r cont_total`** -->

</div>

---

### Time required for plantings:

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
min_groasis <- gro_total*groa_time[1]
min_cocoon <- coc_total*coco_time[1]
min_control <- cont_total*cont_time[1]
total_hrs_minimum <- (min_groasis+min_cocoon+min_control)/60

max_groasis <- gro_total*groa_time[2]
max_cocoon <- coc_total*coco_time[2]
max_control <- cont_total*cont_time[2]
total_hrs_maximum <- (max_groasis+max_cocoon+max_control)/60
```


<div class = "blue">

#### Minimum Person-Hours required (for small sites):
### **`r round(total_hrs_minimum)`** **`r paste("= (4 staff working for", round(total_hrs_minimum/4), "hours)")`**

<br>


#### Maximum+ Person-Hours required (for larger sites and with fences):
### **`r  round(total_hrs_maximum)`** **`r paste("= (4 staff working for", round(total_hrs_maximum/4), "hours)")`**

These time estimates are based are based on general estimates from two different sites (San Cristobal and Baltra) and though they are approximate they are probably close to the realistic number. However, these estimates likely don't apply to sites such as Española where the unique site requires particular effort (e.g., piling rocks up to protect plants, etc.).

</div>

---

### Random order plantings:

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
as.tibble(random_plantings) %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left", font_size = 12)
```







\ 

\ 

\ 


